Hypertension and microbiome

### 2019-05-14 articletwo.Rmd
Genus core missing, cleaner import function

```{r data}
pseq.genus <- readRDS("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
pseq.species <- readRDS("data/phfinrisk_species_all_drop50k_2018-12-21.RDs")
```

Updating phyloseq objects

```{r updating phyloseq objects}
phyloseq::sample_data(pseq.genus) <- phyloseq::sample_data(filter.phenotype.data(pseq.genus))
phyloseq::sample_data(pseq.species) <- phyloseq::sample_data(filter.phenotype.data(pseq.species))
```

Sample data has dimensions (`r dim(sample_data(pseq.species))`).

@@

>>>>

```{r data}
pseq.genus <- import_filter_data("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")
pseq.species <- import_filter_data("data/phfinrisk_species_all_drop50k_2018-12-21.RDs")
```

At species level meta has dimensions (`r dim(meta(pseq.species))`) and
there ntaxa is `r ntaxa(pseq.species)`, and at genus level meta has
dimensions (`r dim(meta(pseq.genus))`) and there ntaxa is `r
ntaxa(pseq.genus)`.

@@

```{r core taxa}
pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
```
